One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-07 doc/genesetdp.tex
Typo
removed  word

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
	  % \includegraphics{figures/calibration_legend.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets. On all plots the dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$, for comparison}
  \label{fig:calibration}
\end{figure}

@@

Here we made an explicit definition of the null hypothesis we employed, which centers on the query, $H_0$ : ``The Q query genes are randomly selected from the genome''. Previous implementations of NEA in the literature otherwise use Monte Carlo-simulation to determine parameters for various types parametric distributions, by perturbations of the investigated network. In practice, such perturbations are hard to conduct in a manner that they still resemble the original network, and hence are difficult to use to calculate accurate statistics. In general, it is easier to understand null models that relate to user actions, than more complex null models that relate to model parameters.

>>>>

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
	  % \includegraphics{figures/calibration_legend.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their {\em normalized rank}, i.e. each $p$~value's (<rank>-0.5)/<total number of $p$~values>. We also added the calibration curve of BinoX, evaluated on the same random sets. On all plots the dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$, for comparison}
  \label{fig:calibration}
\end{figure}

@@

Here we made an explicit definition of the null hypothesis we employed, which centers on the query, $H_0$ : ``The Q query genes are randomly selected from the genome''. Previous implementations of NEA in the literature use Monte Carlo-simulation to determine parameters for various types parametric distributions, by perturbations of the investigated network. In practice, such perturbations are hard to conduct in a manner that they still resemble the original network, and hence are difficult to use to calculate accurate statistics. In general, it is easier to understand null models that relate to user actions, than more complex null models that relate to model parameters.
